Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Small caption edits

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/stimuli_shapes.pdf}
    \vspace{0pt}
    \caption{Example stimuli}
    \label{fig:stimuli}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/likelihood_function.pdf}
    \caption{Likelihood function}
    \label{fig:likelihood}
  \end{subfigure}
  \caption{\textbf{Rotated shapes and their similarity.}  \textbf{(a)}
    An example stimulus in which the shapes differ only by a
    rotation. All stimuli consist of five vertices centered around the
    origin, and four edges which create a closed loop from the
    vertices. \textbf{(b)} The approximate likelihood (similarity) of
    $X_b$ given $X_R$, where $X_R$ is a rotation of $X_a$ by the angle
    $R$. The true angle of rotation between $X_a$ and $X_b$ is
    slightly greater than $\pi$, corresponding to the global maximum
    in the likelihood function.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/Z_accuracy.pdf}
  \caption{\textbf{Accuracy in estimating $Z$.} \TODO{} \TODO{use
      different markers for $h_0$ and $h_1$ points}}
  \label{fig:accuracy}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/stimuli_shapes.pdf}
    \vspace{0pt}
    \caption{Example stimuli}
    \label{fig:stimuli}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/likelihood_function.pdf}
    \caption{Likelihood function}
    \label{fig:likelihood}
  \end{subfigure}
  \caption{\textbf{Rotated shapes and their similarity.}  \textbf{(a)}
    An example stimulus in which the shapes differ only by a
    rotation. All stimuli consist of five vertices centered around the
    origin, and four edges which create a closed loop from the
    vertices. \textbf{(b)} The approximate likelihood (similarity) of
    $X_b$ given $X_R$, where $X_R$ is a rotation of $X_a$ by the angle
    $R$. The true angle of rotation between $X_a$ and $X_b$ is
    approximately $\frac{\pi}{4}$, corresponding to the global maximum
    in the likelihood function.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/Z_accuracy.pdf}
  \caption{\textbf{Accuracy in estimating $Z$.} \TODO{}}
  \label{fig:accuracy}
\end{figure}
